### 2025-01-02 manuscript.tex
Introduction started.

%\documentclass[a4paper,oneside,onecolumn,12pt]{LegrandOrangeBook}
\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\def\magyarOptions{chapterhead=unchanged}
%\usepackage[magyar]{babel}
\usepackage{longtable}
%\usepackage{amsthm}
% \usepackage{amsmath}
% \usepackage{amsfonts}
% \usepackage{txfonts}
% \usepackage{pxfonts}
% %\usepackage{eufrak}
% \usepackage{mathptmx}
\usepackage{setspace}
% \usepackage{graphicx}
\usepackage{parskip} %paragraph között legyen spacing
% \usepackage[export]{adjustbox}%kép pozicionálás
\usepackage{minted}
\usepackage{svg}
% \usepackage{hyperref}
% \usepackage{multimedia}
% \usepackage{wrapfig}
% \usepackage{csquotes}
\usepackage{ragged2e}

@@

@@

% Book information for PDF metadata, remove/comment this block if not required 
% \hypersetup{
% 	pdftitle={Real-time stock market price data analysis using neural networks}, % Title field
% 	pdfauthor={Bc. Eugen Fekete}, % Author field
% 	pdfsubject={Diplomamunka}, % Subject field
% 	pdfkeywords={key1, key2, key3, key4}, % Keywords
% 	pdfcreator={LaTeX}, % Content creator field
% }

% \definecolor{ocre}{RGB}{243, 102, 25} % Define the color used for highlighting throughout the book

% \chapterspaceabove{6.5cm} % Default whitespace from the top of the page to the chapter title on chapter pages
% \chapterspacebelow{6.75cm} % Default amount of vertical whitespace from the top margin to the start of the text on chapter pages

% \onehalfspacing
% %\doublespacing
% \frenchspacing

% \hypersetup{
%     colorlinks=true,
%     linkcolor=blue,
%     filecolor=magenta,      
%     urlcolor=cyan,
%     pdftitle={Real-time stock market price data analysis using neural networks} }
% \urlstyle{same}

% %% \usepackage[backend=biber, style=numeric-comp, sorting=none,]{biblatex}
% %% \PassOptionsToPackage{sorting=none,language=english}{biblatex}
% \ExecuteBibliographyOptions{sorting=none}
% \addbibresource{manuscript.bib}
\begin{document}

@@

\cleardoublepage
\begingroup
\makeatletter
\let\ps@plain\ps@empty
\begin{minipage}[c][\textheight][c]{\textwidth}
	{\centering
	{\large UNIVERZITA J. SELYEHO\\SELYE JÁNOS EGYETEM}\\
	\vskip0.5cm
	{\ NÁZOV FAKULTY\\Fakulta ekonómie a informatiky\\Gazdaságtudományi és Informatikai Kar}\\
	\vfill
	{\Large NÁZOV PRÁCE\\Analýza údajov o cenách na burze v reálnom čase pomocou neurónových sietí }\\
	\vfill
	\thispagestyle{empty}
	\begin{tabular}{ll}
		Študijný program:    & Aplikovaná informatika \\
		Tanulmányi program:  & Alkalmazott Informatika\\
		Študijný odbor:      & Informatika\\
		Tanulmányi szak:     & Informatika\\
		Školiteľ:            & László Marák, PhD.\\
		Témavezető:          & László Marák, PhD.\\
		Konzultant:          & László Marák, PhD. \\
		Konzulens:           & László Marák, PhD.\\
		Školiace pracovisko: & Katedra informatiky\\
		Tanszék megnevezése: & Informatikai Tanszék\\
	\end{tabular}
	\vfill
	Označenie typu práce - Diplomamunka\\
	Bc. Eugen Fekete\\
    \ISBN \\
	\hfill\the\year{}, Komárno\hfill
	}
\end{minipage}
\endgroup
{
\hspace*{-2cm}
%\includegraphics[keepaspectratio, width=17cm]{./zadanie-zp_17422.pdf}
Ide jön az aláírt témakiírás
\pagebreak
}
\tableofcontents %% opcionális
\pagebreak
\listoffigures  %% opcionális
\addcontentsline{toc}{section}{Ábrák jegyzéke}

@@

\newcommand{\chpt}[1]{\chapter*{#1}\addcontentsline{toc}{section}{#1}}
\chapterimage{kep/header.png} % Chapter heading image

@@

%\chapterimage{kep/header2.png} % Chapter heading image
\chpt{Opis práce}
% \addcontentsline{toc}{chapter}{Opis práce}

@@

\chapter*{Bevezetés}
\addcontentsline{toc}{chapter}{Bevezetés}
\markboth{}{\sffamily\normalsize{Bevezetés}}
\begin{eBox}
    Fontos megjegyzés, vagy állítás
\end{eBox}
% \commentaron{szürke háttérrel kicsit fura nekem}\comment{válassz tetszőleges hátteret}

\begin{figure}
  \begin{tBox}
    \centering{\LARGE{\url{https://google.com/}}}
  \end{tBox}
  \caption{Felirat}\label{fig:link}
\end{figure}

Még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hossz

\chapterimage{kep/header2.png} % Chapter heading image
\chapter{Elméleti rész}

Még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hossz

\section{Alfejezet}

Még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hosszabb, még egy kicsit hossz

@@

\chapterimage{kep/header2.png} % Chapter heading image
\chapter{Gyakorlati rész}

@@

\chapterimage{kep/header.png} % Chapter heading image
\chapter*{Befejezés}
\addcontentsline{toc}{chapter}{Befejezés}

@@

\pagebreak
\chapterimage{kep/header3.png} % Chapter heading image
\chapter*{Resumé}
\addcontentsline{toc}{chapter}{Resumé}
\markboth{}{\sffamily\normalsize{Resumé}}

>>>>

\documentclass[a4paper,oneside,onecolumn,12pt]{LegrandOrangeBook}
%\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\def\magyarOptions{chapterhead=unchanged}
%\usepackage[magyar]{babel}
\usepackage{longtable}
%\usepackage{amsthm}
% \usepackage{amsmath}
% \usepackage{amsfonts}
% \usepackage{txfonts}
% \usepackage{pxfonts}
% %\usepackage{eufrak}
% \usepackage{mathptmx}
\usepackage{setspace}
% \usepackage{graphicx}
\usepackage{parskip} %paragraph között legyen spacing
% \usepackage[export]{adjustbox}%kép pozicionálás
\usepackage{minted}
\usepackage{svg}
% \usepackage{hyperref}
% \usepackage{multimedia}
% \usepackage{wrapfig}
% \usepackage{csquotes}
\usepackage{ragged2e}

@@

\usepackage{biblatex} %Imports biblatex package
\addbibresource{manuscript.bib} %Import the bibliography file

@@

% Book information for PDF metadata, remove/comment this block if not required 
\hypersetup{
	pdftitle={Real-time stock market price data analysis using neural networks}, % Title field
	pdfauthor={Bc. Eugen Fekete}, % Author field
	pdfsubject={Diplomamunka}, % Subject field
	pdfkeywords={key1, key2, key3, key4}, % Keywords
	pdfcreator={LaTeX}, % Content creator field
}

\definecolor{ocre}{RGB}{243, 102, 25} % Define the color used for highlighting throughout the book

\chapterspaceabove{6.5cm} % Default whitespace from the top of the page to the chapter title on chapter pages
\chapterspacebelow{6.75cm} % Default amount of vertical whitespace from the top margin to the start of the text on chapter pages

\onehalfspacing
%\doublespacing
\frenchspacing

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Real-time stock market price data analysis using neural networks} }
\urlstyle{same}

%% \usepackage[backend=biber, style=numeric-comp, sorting=none,]{biblatex}
%% \PassOptionsToPackage{sorting=none,language=english}{biblatex}
\ExecuteBibliographyOptions{sorting=none}
\addbibresource{manuscript.bib}
\begin{document}

@@

\cleardoublepage
\begingroup
\makeatletter
\let\ps@plain\ps@empty
\begin{minipage}[c][\textheight][c]{\textwidth}
	{\centering
	{\large UNIVERZITA J. SELYEHO\\SELYE JÁNOS EGYETEM}\\
	\vskip0.5cm
	{\ NÁZOV FAKULTY\\Fakulta ekonómie a informatiky\\Gazdaságtudományi és Informatikai Kar}\\
	\vfill
	{\Large NÁZOV PRÁCE\\Analýza údajov o cenách na burze v reálnom čase pomocou neurónových sietí }\\
	\vfill
	\thispagestyle{empty}
	\begin{tabular}{ll}
		Študijný program:    & Aplikovaná informatika \\
		Tanulmányi program:  & Alkalmazott Informatika\\
		Študijný odbor:      & Informatika\\
		Tanulmányi szak:     & Informatika\\
		Školiteľ:            & László Marák, PhD.\\
		Témavezető:          & László Marák, PhD.\\
		Školiace pracovisko: & Katedra informatiky\\
		Tanszék megnevezése: & Informatikai Tanszék\\
	\end{tabular}
	\vfill
	Označenie typu práce - Diplomamunka\\
	Bc. Eugen Fekete\\
    \ISBN \\
	\hfill\the\year{}, Komárno\hfill
	}
\end{minipage}
\endgroup
{
\hspace*{-2cm}
%\includegraphics[keepaspectratio, width=17cm]{./zadanie-zp_17422.pdf}
Ide jön az aláírt témakiírás
\pagebreak
}
\tableofcontents %% opcionális
\pagebreak
\listoffigures  %% opcionális
\addcontentsline{toc}{section}{Ábrák jegyzéke}

@@

\newcommand{\chpt}[1]{\chapter*{#1}\addcontentsline{toc}{section}{#1}}
% \chapterimage{kep/header.png} % Chapter heading image

@@

% \chapterimage{kep/header2.png} % Chapter heading image
\chpt{Opis práce}
% \addcontentsline{toc}{chapter}{Opis práce}

@@

\chapter*{Bevezetés}
\addcontentsline{toc}{chapter}{Bevezetés}
\markboth{}{\sffamily\normalsize{Bevezetés}}
% \begin{eBox}
%     Fontos megjegyzés, vagy állítás
% \end{eBox}
% \commentaron{szürke háttérrel kicsit fura nekem}\comment{válassz tetszőleges hátteret}

% \begin{figure}
%   \begin{tBox}
%     \centering{\LARGE{\url{https://google.com/}}}
%   \end{tBox}
%   \caption{Felirat}\label{fig:link}
% \end{figure}

Machine learning plays a pivotal role in many areas of modern sciences, whether in industry, healthcare, finance or other fields. It can be used to provide a better service for the users of a search engine, a social media site or a media service provider by learning from the behaviour of the average user, predict stock prices within a specific time interval based on company performance measures and economic data, identify the risk factors for certain health conditions derived from clinical and demographic variables, identify the characters in a handwritten address from a digitized image, and so on. \cite{TESL}

% \chapterimage{kep/header2.png} % Chapter heading image
\chapter{Elméleti rész}

Lorem ipsum dolores

\section{Machine Learning}

@@

% \chapterimage{kep/header2.png} % Chapter heading image
\chapter{Gyakorlati rész}

@@

% \chapterimage{kep/header.png} % Chapter heading image
\chapter*{Befejezés}
\addcontentsline{toc}{chapter}{Befejezés}

@@

\pagebreak
% \chapterimage{kep/header3.png} % Chapter heading image
\chapter*{Resumé}
\addcontentsline{toc}{chapter}{Resumé}
\markboth{}{\sffamily\normalsize{Resumé}}
